\newcommand{\puttitle}[0]{Cogworks - An Environment For Collaborative Cognitive Modelling}

\title{\puttitle}
% Fill the following information to accurately reflect on title page
% NOTE: if you are a PhD student, fill \degree with Doctor of Philosophy
\author{Reuben Francis Cornel}
\degreeyear{2009}
\degree{Master of Science}
\chair{Dr. Robert St. Amant}
\memberII{Dr. Christopher Healey}
\memberIII{Dr. James Lester}
\numberofmembers{3}



\newpage
\thispagestyle{empty}
%Defined construct to puts the word "ABSTRACT" as per requirement...
\abstractname
\vskip .5cm
% EA - The header of the abstract must be single spaced -- add this
% explicitly using \ssp
\ssp
% Use \noindent to ensure the Abstract header is left justified...
\noindent 
Cornel, Reuben F. \puttitle. (Under the direction of Dr. Robert St. Amant).

\renewcommand{\baselinestretch}{2}

\vspace{0.2in}

% EA - The rest of the document should be double spaced
\dsp

Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  

Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  



% EA - If your abstract runs more than one page you will need
% the following lines to force a page break between paragraphs
% and not put a page number on the second (and subsequent)
% pages of your abstract.
%
%\newpage
%\thispagestyle{empty}
%

% EA - Put your field here:  Physics, Mathematics, Statistics, etc.
\field{Computer Science}

% EA - I added ', North Carolina' per thesis editor's
% directions
\campus{Raleigh, North Carolina}

\maketitle

\begin{frontmatter}

\begin{dedication}
\vskip .5cm
\begin{center}
For Mom, Dad and my baby sister Becca.
\end{center}
\end{dedication}

\biographyname
\vskip .5cm
Reuben Francis Cornel was born in Mumbai, India and spent most of his
life in various cities across South India. He received his Bachelor of
Engineering in Computer Science and Engineering from Visweswariah
Technologial University. He is currently pursuing
his Masters in Computer Science at the North Carolina State
University. He is passionate about Computer Science and completely
believes that some day computers will be as smart as humans.

\begin{acknowledgements}
\vskip .5cm
Put your acknowledgements here, some people you may wish to thank: advisors, committee, professors, family, friends, and Santa.

\vskip .5cm

More acknowledgements as needed.
\end{acknowledgements}

\tableofcontents
% MS -- switched the order of list of tables and figures
\newpage
\listoftables
\newpage
\listoffigures

\end{frontmatter}
